Generality in food webs scales with species richness, not latitude

### 2014-07-09 manuscript/latitudepaper.tex
Fixed some of the equation issues.

\begin{equation}

$S_{i} = \alpha_{0} + \alpha_{1}\Delta_{i}+\epsilon_{i}$ \,,

@@

\begin{equation}
\label{Power}
$Z=\alpha S^{\beta} + \epsilon $ \,,
\end{equation}

@@

\begin{equation}
\label{Loglog}
$log(Z) = log(\alpha) + \beta log(S) + \epsilon $ \,.
\end{equation}

@@

\begin{equation}
\label{PowerLat}
$Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}\Tau_{i} + \beta_{6}\Mu_{i} 
+ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}\Tau_{i} + \beta_{10}\Delta_{i}\Mu_{i}}
+ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}\Eta_{i} + P_{i} + \epsilon_{i} $ \,,
\end{equation}

where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
$\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are 
factors indicating whether web $i$ is a stream, lake, 
terrestrial, or marine food web (e.g., $\Sigma_{i}$=1 for 
a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are all 0, web $i$ 
describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $\Eta_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
site ID. Note that all fixed effects $\beta$ refer to factors acting on the scaling exponent between $Z$ and $S$
while fixed effects $\rho$ refer to factors acting on the residual error.

@@

\begin{equation}
\label{LogLat}
$Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}\Tau_{i}log(S)  + \beta_{6}\Mu_{i}log(S)  
+ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}\Tau_{i}log(S)  + \beta_{10}\Delta_{i}\Mu_{i}log(S) 
+ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}\Eta_{i} +\epsilon_{i} $ \,.

>>>>

\begin{eqnarray}
S_{i} = \alpha_{0} + \alpha_{1} \Delta_{i} + \epsilon_{i} 
\end{eqnarray}

@@

\begin{equation}
\label{Power}
Z_{i}=\alpha S_{i}^{\beta} + \epsilon_{i} 
\end{equation}

@@

\begin{equation}
\label{Loglog}
log(Z_{i}) = log(\alpha) + \beta log(S_{i}) + \epsilon_{i}  
\end{equation}

@@

\begin{equation}
\label{PowerLat}

Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}T_{i} + \beta_{6}M_{i} 
+ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}T_{i} + \beta_{10}\Delta_{i}M_{i}}
+ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}H_{i} + P_{i} + \epsilon_{i} 
\end{equation}

where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
$\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are 
factors indicating whether web $i$ is a stream, lake, 
terrestrial, or marine food web (e.g., $\Sigma_{i}$=1 for 
a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are all 0, web $i$ 
describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $H_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
site ID. Note that all fixed effects $\beta$ refer to factors acting on the scaling exponent between $Z$ and $S$
while fixed effects $\rho$ refer to factors acting on the residual error.

@@

\begin{equation}
\label{LogLat}
Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}T_{i}log(S)  + \beta_{6}M_{i}log(S)  
+ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}T_{i}log(S)  + \beta_{10}\Delta_{i}M_{i}log(S) 
+ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}H_{i} +\epsilon_{i}
